% \documentclass[extrafontsizes, letterpaper, 11pt]{memoir} % PRIEST
\documentclass[extrafontsizes, statementpaper, 10pt]{memoir}

% \usepackage{priest}
\usepackage{people}


\begin{document}
\thispagestyle{empty}

\mytitle

\rubric{After the Asperges, kneeling before the altar, the Celebrant intones
the following antiphon:}

\gregorioscore{sub_tuum.gabc}

\rubric{The celebrant blesses the crown, held before him by an acolyte:}

\vbar Adjutórium nostrum in nómine Dómini.\\
\rbar Qui fecit cœlum et terram.\\
\vbar Dóminus vobíscum.\\
\rbar Et cum spíritu tuo.

% \rubric{Oremus.}
\oremus

\lettrine{O}{mnípotens} sempitérne Deus, cujus clementíssima dispensatióne
cuncta creáta sunt ex níhilo, Majestátem tuam súpplices deprecámur : ut hanc corónam pro ornátu Sacræ Imáginis Beatíssimæ Vírginis Maríæ fabricátam bene\Cross dícere, et sancti\Cross ficáre dignéris. Per Christum Dóminum
nostrum.

\rbar Amen.

\rubric{Incense is imposed. The celebrant sprinkles with holy water and
incenses the crown. The celebrant processes with the master of ceremonies,
thurifer and acolyte to the statue of the Blessed Virgin Mary, where he kneels
and intones:}

% \pagebreak use for 14 pt

\gregorioscore{regina}

\rubric{While the chanters continue the antiphon \textit{\color{black} Regina
Cœli,} the celebrant crowns the statue saying:}

% {\huge
% \lettrine{S}{icuti} per manus nostras coronáris in terris, ita et per te a Jesu
% Christo Fílio tuo glória atque honóre coronári mereámur in cœlis.
% }

\textbf{\huge Sícuti per manus nostras coronáris in terris, ita et per te a
Jesu Christo Fílio tuo glória atque honóre coronári mereámur in cœlis.}

\rubric{Once the statue is crowned, the celebrant incenses the image with three
double swings, standing, making a medium bow before and after. Once the
chanters have finished the antiphon, or after incensing the statue, the
celebrant, standing, chants:}

\vbar Gaude et lætáre, Virgo María, allelúja.\\
\rbar Quia surréxit Dóminus vere, allelúja.

% \rubric{Oremus.}
\oremus

\lettrine{D}{eus,} qui per resurrectiónem Fílii tui, Dómini nostri Jesu
Christi, mundum lætificáre dignátus es : præsta, quǽsumus; ut, per ejus
Genitrícem Vírginem Maríam, perpétuæ capiámus gáudia vitæ. Per eúmdem Christum
Dóminum nóstrum. 

\rbar Amen.

% \pagebreak use for 14 pt

\rubric{The celebrant, kneeling, now makes the Act of Consecration:}

\lettrine{O}{} Mary, Virgin most powerful and Mother of Mercy, Queen of Heaven
and Refuge of sinners, we consecrate ourselves to thine Immaculate Heart. We
consecrate to thee our very being and our whole life; all that we have, all
that we love, all that we are. To thee we give our homes, our families, our
country.

\lettrine{W}{e} desire that all that is in us and around us may belong to thee,
and may share in the benefits of thy Motherly blessing.

\lettrine{A}{nd} that this act of consecration may be truly efficacious and
lasting, we renew this day at thy feet the promises of our baptism and our
first Holy Communion.

\lettrine{W}{e} pledge ourselves to profess bravely and at all time the truths
of our Holy Faith, and to live as befits Catholics. We pledge ourselves to keep
the commandments of God and His Holy Church; in particular to keep holy the
Lord’s Day. We likewise pledge ourselves to make the consoling practices of the
Christian religion, and above all Holy Communion, a central part of our lives,
in so far as we shall be able to do so.

\lettrine{F}{inally,} we promise thee, O Glorious Mother of God and loving
Mother of men, to devote ourselves whole heartedly to the service of thy
blessed veneration in order to hasten and assure, through the Queenship of
thine Immaculate Heart the coming of the Kingdom of the Sacred Heart of thy
dear Son in our hearts and in those of all men, in our country and in all the
world, as in heaven so on earth. 

\rbar Amen.

\rubric{Concluding hymn: \textit{\color{black} Salve Regina.}}


    
\end{document}
