\documentclass[statementpaper, 11pt]{memoir}

\usepackage{liturgicalbooklet} % still a work in progress

\mytitle{First Friday Devotion}{sacredheart}

\renewcommand{\LettrineFontHook}{\fontfamily{lmr}\color{gregoriocolor}}

\usepackage{verse}

\begin{document}

\maketitle

% TODO: make the title

\begin{verse}

O salut\'aris H\'ostia,\\
Qu\ae\ c\ae li pandis \'ostium:\\
Bella premunt host\'ilia,\\
Da robur, fer aux\'ilium.

Uni trin\'oque D\'omino\\
Sit sempit\'erna gl\'oria,\\
Qui vitam sine t\'ermino\\
Nobis donet in p\'atria.\\
Amen.
    
\end{verse}

\subsection{Act of Reparation to the Sacred Heart of Jesus}

\inlinerubric{Priest and people:} O Sweet Jesus, * whose overflowing charity
for men * is requited by so much forgetfulness, negligence, and contempt, *
behold us prostrate before Thy altar * eager to repair by a special act of
homage * the cruel indifference and injuries, * to which Thy loving Heart is
everywhere subject. * Mindful alas! that we ourselves have had a share in such
great indignities, * which we now deplore from the depths of our hearts, * we
humbly ask Thy pardon and declare our readiness * to atone by voluntary
expiation * not only for our own personal offenses, * but also for the sins of
those, who, * straying far from the path of salvation, * refuse in their
obstinate infidelity to follow Thee, their Shepherd and Leader, * or,
renouncing the vows of their baptism, * have cast off the sweet yoke of Thy
law. * We are now resolved * to expiate each and every deplorable outrage
committed against Thee; * we are determined to make amends * for the manifold
offenses against Christian modesty in unbecoming dress and behavior, * for all
the foul seductions laid to ensnare the feet of the innocent, * for the
frequent violation of Sundays and holydays, * and the shocking blasphemies
uttered against Thee and Thy saints. * We wish also to make amends for the
insults to which Thy priests are subjected, * for the profanation, * by
conscious neglect or terrible acts of sacrilege, * of the very Sacrament of Thy
divine love; * and lastly for the public crimes of nations * who resist the
rights and teaching authority of the Church which Thou hast founded. * Would, O
divine Jesus, * we were able to wash away such abominations with our blood. *
We now offer, * in reparation for these violations of Thy divine honor, * the
satisfaction Thou didst once make * to Thy Eternal Father on the cross * and
which Thou dost continue to renew daily on our altars; * we offer it in union
with the acts of atonement of Thy Virgin Mother and all the Saints * and of the
pious faithful on earth; * and we sincerely promise to make reparation, * as
far as we can with the help of Thy grace, * for all neglect of Thy great love *
and for the sins we and others have committed in the past. * Henceforth we will
live a life of unwavering faith, * of purity of conduct, * of perfect
observance of the precepts of the gospel * and especially that of charity. * We
promise to the best of our power * to prevent others from offending Thee * and
to bring as many as possible to follow Thee. * O loving Jesus, * through the
intercession of the Blessed Virgin Mary * our model in reparation, * deign to
receive the voluntary offering we make of this act of expiation; * and by the
crowning gift of perseverance * keep us faithful unto death in our duty * and
the allegiance we owe to Thee * so that we may all one day come to that happy
home, * where Thou with the Father and the Holy Ghost * livest and reignest
God, * world without end. Amen.

\rubric{The Litany of the Sacred Heart is sung or recited.}

\subsection{Litany of the Sacred Heart of Jesus}

Lord, have mercy on us.\\
Lord, have mercy on us.\\
Christ, have mercy on us.\\
Christ, have mercy on us.\\
Lord, have mercy on us.\\
Lord, have mercy on us.\\
Christ, hear us.\\
Christ, hear us.\\
Christ, graciously hear us.\\
Christ, graciously hear us.\\
God, the Father of Heaven,\\
God, the Son, Redeemer of the world, God, the Holy Ghost, Holy Trinity, one God,\\
Heart of Jesus, Son of the eternal Father,\\
Heart of Jesus, formed by the Holy Ghost in the womb of the Virgin Mother,\\
Heart of Jesus, substantially united to the Eternal Word,\\
Heart of Jesus, of Infinite Majesty,\\
Heart of Jesus, Holy Temple of God,\\
Heart of Jesus, Tabernacle of the Most High,\\
Heart of Jesus, House of God and Gate of Heaven,\\
Heart of Jesus, burning furnace of Charity,\\
Heart of Jesus, abode of Justice and Love,\\
Heart of Jesus, full of Goodness and Love,\\
Heart of Jesus, abyss of all virtues,\\
Heart of Jesus, most worthy of all praise,\\
Heart of Jesus, King and Center of all hearts,\\
Heart of Jesus, in whom are all the treasures of wisdom and knowledge,\\
Heart of Jesus, in Whom dwells the fullness of the Divinity,\\
Heart of Jesus, in Whom the Father was well pleased,\\
Heart of Jesus, of Whose fullness we have all received,\\
Heart of Jesus, desire of the everlasting hills,\\
Heart of Jesus, patient and most merciful,\\
Heart of Jesus, enriching all who invoke Thee,\\
Heart of Jesus, fountain of life and holiness,\\
Heart of Jesus, propitiation for our sins,\\
Heart of Jesus, loaded down with reproaches,\\
Heart of Jesus, bruised for our offenses,\\
Heart of Jesus, obedient unto death,\\
Heart of Jesus, pierced with a lance,\\
Heart of Jesus, source of all consolation,\\
Heart of Jesus, our life and resurrection,\\
Heart of Jesus, our peace and reconciliation,\\
Heart of Jesus, Victim for sin,\\
Heart of Jesus, salvation of those who trust in Thee,\\
Heart of Jesus, hope of those who die in Thee,\\
Heart of Jesus, delight of all the Saints,\\
Lamb of God, who takest away the sins of the world, Spare us, O Lord.\\
Lamb of God, who takest away the sins of the world, Graciously hear us, O Lord.\\
Lamb of God, who takest away the sins of the world, Have mercy on us.\\
\vbar Jesus meek and humble of Heart, \\
\rbar Make our hearts like unto Thine.

\rubric{Let us pray:}

\lettrine{A}{lmighty} and Eternal God, look upon the Heart of Thy dearly beloved son, and
upon the praise and saistaction, He offers Thee in the name of sinners and for
those who seek Thy mercy; be Thou appeased, and grant us pardon in the name of
the same Jesus Christ, Thy Son, Who liveth and reigneth with Thee, in the unity
of the Holy Ghost, world without end.\\
\rbar Amen.

\subsection{Consecration of the Human Race to the Sacred Heart of Jesus}

\inlinerubric{Priest and people:}Most Sweet Jesus, * Redeemer of the human race, * look down
upon us humbly prostrate before Thy Altar. * We are Thine, and Thine we wish to
be; * but to be more surely united with Thee, behold each one of us freely
consecrates himself today to Thy Most Sacred Heart. * Many indeed have never
known Thee; * many too, despising Thy precepts, have rejected Thee. * Have
mercy on them all, most merciful Jesus, * and draw them to Thy Sacred Heart. *
Be Thou King, O Lord, * not only of the faithful who have never forsaken Thee,
* but also of the prodigal children who have abandoned Thee; * grant that they
may quickly return to their Father's house * lest they die of wretchedness and
hunger. * Be Thou King of those who are deceived by erroneous opinions, * or
whom discord keeps aloof, * and call them back to the harbor of truth and unity
of faith, * so that soon there may be but one flock and one Shepherd Be Thou
King of all those who are still involved in the darkness of idolatry or of
Islamism, * and refuse not to draw them all into the light and kingdom of God.
* Turn Thine eyes of mercy towards the children of that race, * once Thy chosen
people. * Of old they called down upon themselves the Blood of the Saviour; *
may It now descend upon them a laver of redemption and of life. * Grant, O
Lord, to Thy Church assurance of freedom and immunity from harm; * give peace
and order to all nations, * and make the earth resound from pole to pole with
one cry: * Praise to the Divine Heart that wrought our salvation; * to It be
glory and honor forever. Amen.

\rubric{If All Night Adoration is to follow, at this point the celebrant
retires to the sacristy. The Devotions are concluded on the following
morning.\\ If there will not be All Night Adoration, there is a period of
private prayer, followed by the hymn \textit{\black{Tantum Ergo}} and the other
prayers that follow.}

\begin{verse}
    
Tantum ergo Sacram\'entum\\
Vener\'emur c\'ernui\\
Et ant\'iquum docum\'entum,\\
Novo cedat r\'itui,\\
Pr\ae stet fides supplem\'entum\\
S\'ensuum def\'ectui.

Genit\'ori, genit\'oque,\\
Laus et jubil\'atio;\\
Salus, honor, virtus quoque\\
Sit et bened\'ictio.\\
Proced\'enti ab utr\'oque\\
Compar sit laud\'atio. Amen\\

\end{verse}

\vbar Panem de c\ae lo pr\ae stit\'isti eis. (T. P. Allel\'uia)\\
\rbar Omne delectam\'entum in se hab\'entem. (T. P. Allel\'uia)

\rubric{Orémus}

\lettrine{D}{eus,} qui nobis sub Sacraménto mirábili passiónis tuae memóriam
reliquísti; tríbue, quaésumus, ita nos Córporis et Sánguinis tui sacra mystéria
venerári, ut redemptiónis tuae fructum in nobis júgiter sentiámus: Qui vivis et
regnas in s\'\ae cula s\ae cul\'orum.\\
\rbar Amen.

\subsection{The Divine Praises}

Blessed be God.\\
Blessed be His holy Name.\\
Blessed be Jesus Christ, true God and true Man.\\
Blessed be the name of Jesus.\\
Blessed be His Most Sacred Heart.\\
Blessed be Jesus in the Most Holy Sacrament of the Altar,\\
Blessed be the great Mother of God, Mary most holy.\\
Blessed be her holy and immaculate Conception.\\
Blessed be her glorious Assumption.\\
Blessed be the name of Mary, Virgin and Mother.\\
Blessed be St. Joseph, her most chaste spouse.\\
Blessed be God in His angels and in His Saints.\\
    
\end{document}
