% \documentclass[extrafontsizes, letterpaper, 11pt]{memoir} % PRIEST
\documentclass[extrafontsizes, statementpaper, 10pt]{memoir}

\setlength\parindent{0pt}

% \usepackage{priest}
\usepackage{people}
\usepackage{parallel}
\usepackage[latin, american]{babel}

\newcommand\verses[2]{
    \ParallelLText{
    \selectlanguage{latin}
    #1
    }
    \ParallelRText{
    \selectlanguage{american}
    #2
    }
    \ParallelPar
}

\begin{document}
\thispagestyle{empty}

\mytitle

\gregorioscore{Veni.gabc}

\begin{center}
    Come, Holy Ghost, Creator blest,\\
    And in our souls take up Thy rest,\\
    Come with thy grace and heavenly aid,\\
    And fill the hearts which Thou hast made.
\end{center}

\begin{Parallel}[c]{}{}

\verses{
Qui d\'iceris Par\'aclitus,\\
Alt\'issimi donum Dei,\\
Fons vivus, ignis, c\'aritas,\\
Et spirit\'alis \'unctio.
}{
To Thee, the Comforter, do we cry,\\
To Thee, the gift of God most high,\\
The fount of life, the fire of love,\\
The soul’s anointing from above.
}

\verses{
Tu, septif\'ormis m\'unere,\\
D\'ig\textit{i}tus pat\'ern\ae\ d\'exter\ae ,\\
Tu rite prom\'issum Patris,\\
Serm\'one ditans g\'uttura.
}{
The sevenfold gifs of grace are Thine,\\
O Finger of the hand Divine;\\
True promise of the Father Thou,\\
Who dost the tongue with speech endow.
}

\verses{
Acc\'ende lumen s\'ensibus:\\
Inf\'und\textit{e} am\'orem c\'ordibus:\\
Inf\'irma nostri c\'orporis\\
Virt\'ute firmans p\'erpeti.
}{
Thy light to every thought impart,\\
And shed Thy love in every heart;\\
Our body’s poor infirmity\\
With strength perpetual fortify.
}

\verses{
Hostem rep\'ellas l\'ongius,\\
Pac\'emque dones pr\'otinus:\\
Duct\'ore sic te pr\'\ae vio\\
Vit\'emus omne n\'oxium.
}{
Our mortal foe afar repel,\\
Grant us henceforth in peace to dwell;\\
If though be our preventing guide,\\
No evil can our steps betide.
}

\verses{
Per te sci\'amus da Patrem,\\
Nosc\'amus atque F\'ilium;\\
Tequ\textit{e} utri\'usque Sp\'iritum\\
Cred\'amus omni t\'empore.
}{
Make Thou to us the Father known;\\
Teach us th’ Eternal Son to own,\\
And Thee, Whose name we ever bless,\\
Of Both the Spirit to confess.
}

\verses{
Deo Patri sit gl\'oria,\\
Et F\'ilio, qu\textit{i} a m\'ortuis\\
Surr\'exit, ac Par\'aclito,\\
In s\ae cul\'orum s\ae cula.
Amen.
}{
All glory while the ages run\\
Be to the Father and the Son,\\
Who rose from death; the same to Thee,\\
O Holy Ghost, eternally.
Amen.
}

% \rubric{The celebrant blesses the crown, held before him by an acolyte:}

\verses{
\vbar Em\'itte Sp\'iritum tuum et creab\'untur; \\
\rbar Et renov\'abis f\'aciem t\'err\ae . \\
}{
\vbar Send forth Thy Spirit and they shall be created; \\
\rbar And Thou shalt renew the face of the earth. \\
}

\verses{
\oremus
}{
\LetUsPray
}

\verses{
\setlength{\linewidth}{\hsize}\lettrine{D}{eus,} qui corda fid\'elium Sancti
Sp\'iritus illustrati\'one docu\'isti: da nobis in e\'odem Sp\'iritu recta s\'apere; et de
ejus semper consolati\'one guad\'ere. Per Christum D\'ominum nostrum.
}{
\setlength{\linewidth}{\hsize}\lettrine{O}{ God,} who didst teach the hearts of
Thy faithful by sending them the light of Thy Holy Ghost, grant us by the same
Spirit to have right judgment of all things, and evermore to rejoice in His
consolation. Through Christ our Lord.
}

\verses{
\rbar Amen.
}{
\rbar Amen.
}

\end{Parallel}

\vfill

{\small 
    An indulgence of 10 years on any day of the novena;

    A plenary indulgence, if they take part in at least five of the exercises,
    and moreover go to confession, receive Holy Communion and pray for the Holy
    Father's intention.
}

\rubric{\footnotesize (Pius IX, Audience, Jan. 3, 1849; S. C. of Bishops and Regulars, Jan.
28, 1850; S. C. Ind., 26, 1876; Brief, May 5, 1859; Encyclical Letter ``Divinum
illud munus'', May 9, 1897; S. P. Ap., May 12, 1934.)}

\end{document}
